Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-04 paper/paper.qmd
commit changes to paper.qmd for formatting

## Posterior Predictive Check for the Trump Model
The posterior predictive check for the Trump model is illustrated @fig-trump-check, showcasing the relationship between the observed support percentages $y$ and the predicted support values $y_{\text{rep}}$. The plot displays a density estimate for both the actual observed data (in dark blue) and the predicted values generated by the model (in light blue). The primary aim of this diagnostic check is to assess how well the model captures the distribution of observed support for Donald Trump.
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-trump-check
#| fig-cap: "Posterior predictive check for Donald Trump's model, illustrating the distribution of observed support percentages $y$ alongside the predicted support values $y_{\text{rep}}$. The graph shows a strong overlap between the observed and predicted distributions, indicating that the model accurately captures the dynamics of voter support for Trump."

@@

print(pp_check_trump)
```
From the visualization, we can observe that the predicted values closely align with the actual observed support percentages. The dark blue curve representing the observed data indicates a concentrated support range around 48% to 52%, suggesting that the model effectively captures the central tendency of voter support for Trump. The light blue curves depict a variety of predicted densities, indicating the model's ability to simulate a range of possible outcomes around the observed values. The alignment of the $y$ and $y_{\text{rep}}$ distributions indicates that the model is successfully reflecting the dynamics of voter support, thereby validating the choice of model and its structure. However, the presence of some variability in the predicted values suggests that while the model fits the observed data well, there may still be unexplained fluctuations in support levels that could warrant further investigation. These limitations are further discussed in @sec-model-diagnostics. This examination enhances our confidence in the model’s utility for forecasting electoral outcomes, ensuring it is robust enough to inform strategic decisions as the election approaches.

>>>>

## Posterior Predictive Check for the Trump Model
```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-trump-check
#| fig-cap: "Posterior predictive check for Donald Trump's model, illustrating the distribution of observed support percentages $y$ alongside the predicted support values $y_{\text{rep}}$. The graph shows a strong overlap between the observed and predicted distributions, indicating that the model accurately captures the dynamics of voter support for Trump."

@@

print(pp_check_trump)
```
The posterior predictive check for the Trump model is illustrated @fig-trump-check, showcasing the relationship between the observed support percentages $y$ and the predicted support values $y_{\text{rep}}$. The plot displays a density estimate for both the actual observed data (in dark blue) and the predicted values generated by the model (in light blue). The primary aim of this diagnostic check is to assess how well the model captures the distribution of observed support for Donald Trump. @fig-trump-check reveals that the predicted values closely align with the actual observed support percentages. The dark blue curve representing the observed data indicates a concentrated support range around 48% to 52%, suggesting that the model effectively captures the central tendency of voter support for Trump. The light blue curves depict a variety of predicted densities, indicating the model's ability to simulate a range of possible outcomes around the observed values. The alignment of the $y$ and $y_{\text{rep}}$ distributions indicates that the model is successfully reflecting the dynamics of voter support, thereby validating the choice of model and its structure. However, the presence of some variability in the predicted values suggests that while the model fits the observed data well, there may still be unexplained fluctuations in support levels that could warrant further investigation. These limitations are further discussed in @sec-model-diagnostics. This examination enhances our confidence in the model’s utility for forecasting electoral outcomes, ensuring it is robust enough to inform strategic decisions as the election approaches.
